Reparametrization of COM-Poisson Regression Models with Applications in the Analysis of Experimental Data

### 2017-11-06 article.Rnw
Divide tables to fit on page and modify to right alignment

%-------------------------------------------
% Document class
\documentclass[submit]{smj}

%-------------------------------------------
% Personal packages and definitions
\usepackage{amsfonts}
\usepackage{bm}
\DeclareRobustCommand{\rchi}{{\mathpalette\irchi\relax}}
\newcommand{\irchi}[2]{\raisebox{\depth}{$#1\chi$}}

@@

\usepackage{float}

@@

\makeatletter
\def\and{%
  \end{tabular}%
  \hskip 0em \@plus.17fil \protect$\bullet$
  \begin{tabular}[t]{c}}%
\makeatother

@@

@@

# Remove excessive scientific notation
xt2 <- gsub("e\\+00", "    ", format(xt))
xt2 <- gsub("\\|([0-9].{2}) \\|", "\\|**\\1** \\|", xt2)
print(xtable(xt2, digits = -2,
             caption = caption,
             align = "C|CCCCCC",
             # align = "ccccccc",
             label = "tab:convergenceZ"),
      include.colnames = FALSE,
      tabular.environment = "tabularx",
      width = "\\textwidth",
      add.to.row = list(
          pos = list(0, 0),
          command = c(
              " \\multicolumn{7}{c}{$\\bm{\\lambda}$} \\\\\n",
              "$\\bm{\\nu}$ & 0.5 & 1 & 5 & 10 & 30 & 50 \\\\\n")
      ))

@@

\begin{table}[!ht]
\centering \small
\caption{Parameter estimates (Est) and ratio between estimate and
  standard error (SE) for the four model strategies for the cotton
  experiment.}
\label{tab:coef-cotton}
\begin{tabularx}{\textwidth}{lrrrrrrrr}
  \toprule
  & \multicolumn{2}{c}{Poisson} &
    \multicolumn{2}{c}{COM-Poisson} &
    \multicolumn{2}{c}{COM-Poisson$_\mu$} &
    \multicolumn{2}{c}{Quasi-Poisson} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
<<results-cotton, results="asis">>=

@@

@
\end{tabularx}
\end{table}

@@

# Organize on table
rownames(corr.ncap) <- paste0("COM-Poisson", c("", "$_\\mu$"))
colnames(corr.ncap) <- gsub("beta", "hat{\\\\beta}", pnames[-1])

caption <- paste("Empirical correlations between $\\hat{\\phi}$ and",
                 "$\\hat{\\bm{\\beta}}$ for the two parametrizations",
                 "of COM-Poisson model fit to underdispersed data.")
print(xtable(corr.ncap,
             align = c("lccccccccccc"),
             caption = caption,
             digits = 3,
             label = "tab:corr-cotton"),
      size = "small",
      sanitize.rownames.function = identity,
      sanitize.colnames.function = function(x) sprintf("$%s$", x))

@@

@@

\begin{table}[!ht]
\centering \small
\caption{Parameter estimates (Est) and ratio between estimate and
  standard error (SE) for the four model strategies for the soybean
  experiment.}
\label{tab:coef-soy}
\begin{tabularx}{\textwidth}{lrrrrrrrr}
  \toprule
  & \multicolumn{2}{c}{Poisson} &
    \multicolumn{2}{c}{COM-Poisson} &
    \multicolumn{2}{c}{COM-Poisson$_\mu$} &
    \multicolumn{2}{c}{Quasi-Poisson} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
<<results-soya, results="asis">>=

@@

## Organize on table
rownames(corr.ngra) <- paste0("COM-Poisson", c("", "$_\\mu$"))
colnames(corr.ngra) <- gsub("(beta|tau|gamma)", "hat{\\\\\\1}",
                            pnames[-1])

caption <- paste("Empirical correlations between $\\hat{\\phi}$ and",
                 "$\\hat{\\bm{\\beta}}$ for the two parametrizations",
                 "of COM-Poisson model fit to overdispersed data.")
print(xtable(corr.ngra,
             align = c("lccccccccccc"),
             caption = caption,
             digits = 3,
             label = "tab:corr-soy"),
      size = "small",
      sanitize.rownames.function = identity,
      sanitize.colnames.function = function(x) sprintf("$%s$", x))

@@

@@

\begin{table}[!ht]
\centering \small
\caption{Model fit measures and comparisons between predictors and models.}
\label{tab:anova-ovos}
\begin{tabularx}{\textwidth}{lcccccrc}
  \toprule
 Poisson & np & $\ell$ & AIC & 2(diff $\ell$) & diff np & P($>\rchi^2$) & \\
 \midrule
<<anova-ovos1, results="asis">>=

@@

@
 \bottomrule
\end{tabularx}
\vspace{-1mm}

@@

\begin{table}[!ht]
\centering
\caption{Parameter estimates (Est) and ratio between estimate and
  standard error (SE) for the four model strategies for the nitrofen
  experiment.}
\label{tab:coef-ovos}
\begin{tabularx}{\textwidth}{lCCCCCCCC}
  \toprule
  & \multicolumn{2}{c}{Poisson} &
    \multicolumn{2}{c}{COM-Poisson} &
    \multicolumn{2}{c}{COM-Poisson$_\mu$} &
    \multicolumn{2}{c}{Quasi-Poisson} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
<<coef-ovos, results="asis">>=

@@

caption <- paste("Empirical correlations between $\\hat{\\phi}$ and",
                 "$\\hat{\\bm{\\beta}}$ for the two parametrizations",
                 "of COM-Poisson model fit to equidispersed data.")
print(xtable(corr.ovos,
             align = c("lCCCC"),
             caption = caption,
             digits = 3,
             label = "tab:corr-ovos"),
      # size = "small",
      sanitize.rownames.function = identity,
      sanitize.colnames.function = function(x) sprintf("$%s$", x),
      tabular.environment = "tabularx",
      width = "\\textwidth")

>>>>

%-------------------------------------------
% Document class
\documentclass[publish]{smj}

%-------------------------------------------
% Personal packages and definitions
\usepackage{amsfonts}
\usepackage{float}
\usepackage{bm}
\DeclareRobustCommand{\rchi}{{\mathpalette\irchi\relax}}
\newcommand{\irchi}[2]{\raisebox{\depth}{$#1\chi$}}

@@

@@

@@

divide_matrix <- function(mat, divide) {
    mat1 <- mat[, 1:divide]
    mat2 <- mat[, (divide + 1):ncol(mat)]
    nc1 <- ncol(mat1)
    nc2 <- ncol(mat2)
    cdiff <- abs(ncol(mat1) - ncol(mat2))
    if (cdiff) {
        complete <- matrix(NA, nrow = nrow(mat), ncol = cdiff)
        colnames(complete) <- rep(" ", cdiff)
        if (nc1 < nc2) {
            mat1 <- cbind(mat1, complete)
        } else {
            mat2 <- cbind(mat2, complete)
        }
    }
    return(list(mat1, mat2))
}

@@

# Remove excessive scientific notation
xt2 <- gsub("e\\+00", "    ", format(xt))
xt2 <- gsub("\\|([0-9].{2}) \\|", "\\|**\\1** \\|", xt2)
print(xtable(xt2, digits = -2,
             caption = caption,
             align = "C|CCCCCC",
             # align = "c|cccccc",
             label = "tab:convergenceZ"),
      include.colnames = FALSE,
      tabular.environment = "tabularx",
      width = "\\textwidth",
      add.to.row = list(
          pos = list(0, 0),
          command = c(
              " \\multicolumn{7}{c}{$\\bm{\\lambda}$} \\\\\n",
              "$\\bm{\\nu}$ & 0.5 & 1 & 5 & 10 & 30 & 50 \\\\\n")
      ))

@@

\begin{table}[!ht]
\centering \small
\caption{Parameter estimates (Est) and ratio between estimate and
  standard error (SE) for the four model strategies for the cotton
  experiment.}
\label{tab:coef-cotton}
\begin{tabular}{lrrrrrrrr}
  \toprule
  & \multicolumn{2}{c}{Poisson} &
    \multicolumn{2}{c}{COM-Poisson} &
    \multicolumn{2}{c}{COM-Poisson$_\mu$} &
    \multicolumn{2}{c}{Quasi-Poisson} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
<<results-cotton, results="asis">>=

@@

@
\end{tabular}
\end{table}

@@

# Organize on table
rownames(corr.ncap) <- paste0("COM-Poisson", c("", "$_\\mu$"))
colnames(corr.ncap) <- gsub("beta", "hat{\\\\beta}", pnames[-1])
corrncap_aux <- divide_matrix(corr.ncap, divide = 6)

# caption <- paste("Empirical correlations between $\\hat{\\phi}$ and",
#                  "$\\hat{\\bm{\\beta}}$ for the two parametrizations",
#                  "of COM-Poisson model fit to underdispersed data.")
# print(xtable(corr.ncap,
#              align = c("lrrrrrrrrrrr"),
#              caption = caption,
#              digits = 3,
#              label = "tab:corr-cotton"),
#       size = "small",
#       sanitize.rownames.function = identity,
#       sanitize.colnames.function = function(x) sprintf("$%s$", x))

@@

\begin{table}[ht]
\centering
\caption{Empirical correlations between $\hat{\phi}$ and $\hat{\bm{\beta}}$ for the two parametrizations of COM-Poisson model fit to equidispersed data.}
\label{tab:corr-cotton}
\begingroup\small
\begin{tabular}{lrrrrrr}
  \toprule
<<results="asis">>=

print(xtable(corrncap_aux[[1]], digits = 4),
      only.contents = TRUE,
      hline.after = FALSE,
      sanitize.colnames.function = function(x) sprintf("$%s$", x))
cat("\\midrule", sep = "\n")

print(xtable(corrncap_aux[[2]], digits = 4),
      only.contents = TRUE,
      sanitize.colnames.function = function(x) sprintf("$%s$", x))

@
\end{tabular}
\endgroup
\end{table}

@@

\begin{table}[!ht]
\centering \small
\caption{Parameter estimates (Est) and ratio between estimate and
  standard error (SE) for the four model strategies for the soybean
  experiment.}
\label{tab:coef-soy}
\begin{tabular}{lrrrrrrrr}
  \toprule
  & \multicolumn{2}{c}{Poisson} &
    \multicolumn{2}{c}{COM-Poisson} &
    \multicolumn{2}{c}{COM-Poisson$_\mu$} &
    \multicolumn{2}{c}{Quasi-Poisson} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
<<results-soya, results="asis">>=

@@

## Organize on table
rownames(corr.ngra) <- paste0("COM-Poisson", c("", "$_\\mu$"))
colnames(corr.ngra) <- gsub("(beta|tau|gamma)", "hat{\\\\\\1}",
                            pnames[-1])
corrngra_aux <- divide_matrix(corr.ncap, divide = 7)

# caption <- paste("Empirical correlations between $\\hat{\\phi}$ and",
#                  "$\\hat{\\bm{\\beta}}$ for the two parametrizations",
#                  "of COM-Poisson model fit to overdispersed data.")
# print(xtable(corr.ngra,
#              align = c("lccccccccccc"),
#              caption = caption,
#              digits = 3,
#              label = "tab:corr-soy"),
#       size = "small",
#       sanitize.rownames.function = identity,
#       sanitize.colnames.function = function(x) sprintf("$%s$", x))

@@

\begin{table}[ht]
\centering
\caption{Empirical correlations between $\hat{\phi}$ and $\hat{\bm{\beta}}$ for the two parametrizations of COM-Poisson model fit to overdispersed data.}
\label{tab:corr-soy}
\begingroup\small
\begin{tabular}{lrrrrrrr}
  \toprule
<<results="asis">>=

print(xtable(corrngra_aux[[1]], digits = 4),
      only.contents = TRUE,
      hline.after = FALSE,
      sanitize.colnames.function = function(x) sprintf("$%s$", x))
cat("\\midrule", sep = "\n")

print(xtable(corrngra_aux[[2]], digits = 4),
      only.contents = TRUE,
      sanitize.colnames.function = function(x) sprintf("$%s$", x))

@
\end{tabular}
\endgroup
\end{table}

@@

\begin{table}[!ht]
\centering \small
\caption{Model fit measures and comparisons between predictors and models.}
\label{tab:anova-ovos}
\begin{tabularx}{\textwidth}{lCCCCCrC}
  \toprule
 Poisson & np & $\ell$ & AIC & 2(diff $\ell$) & diff np & P($>\rchi^2$) & \\
 \midrule
<<anova-ovos1, results="asis">>=

@@

@
 \bottomrule
\end{tabularx}
%\vspace{-1mm}

@@

\begin{table}[!ht]
\centering
\caption{Parameter estimates (Est) and ratio between estimate and
  standard error (SE) for the four model strategies for the nitrofen
  experiment.}
\label{tab:coef-ovos}
\begin{tabular}{lrrrrrrrr}
  \toprule
  & \multicolumn{2}{c}{Poisson} &
    \multicolumn{2}{c}{COM-Poisson} &
    \multicolumn{2}{c}{COM-Poisson$_\mu$} &
    \multicolumn{2}{c}{Quasi-Poisson} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9}
<<coef-ovos, results="asis">>=

@@

caption <- paste("Empirical correlations between $\\hat{\\phi}$ and",
                 "$\\hat{\\bm{\\beta}}$ for the two parametrizations",
                 "of COM-Poisson model fit to equidispersed data.")
print(xtable(corr.ovos,
             align = c("lrrrr"),
             caption = caption,
             digits = 4,
             label = "tab:corr-ovos"),
      # size = "small",
      sanitize.rownames.function = identity,
      sanitize.colnames.function = function(x) sprintf("$%s$", x),
      # width = "\\textwidth,"
      tabular.environment = "tabular")
